\section{Omniprediction for multiple quantile level forecasts}\label{sec:multi_q}
In this section, we extend the result from Section \ref{sec:single_q} to multiple quantile levels. To avoid redundancy, we mainly provide online algorithm for omniprediction of multiple quantile level forecasts. Batch version can be straightforwardly extended from the single quantile level case. The omniprediction objective we want to minimize is given by
\[
\sup_{S \in \cs,\, f \in \cf} \frac{1}{T} \sum_{t=1}^T \E_{p \sim \hat{P}} [S(p, Y_t)] - \E[S(f_t, Y_t)]
\]
where $\cs$ is the class of \textit{all} scoring functions that are consistent for the multiple quantile levels and $\cf$ is a set of competitors.

Section \ref{subsec:decomp_multi_q} discusses the previous result from \cite{fissler2016multiq} on decomposition of consistent scoring rules for multiple quantile levels. Section \ref{subsec:separate_multi_q} shows the cases where post-sorting after solving separate minimax programs for each quantile level works and the cases where it fails, which necessitates the need for solving the minimax program \eqref{eq:omni-twoplayer-minimax} jointly across all quantile levels. Section \ref{subsec:omni_multi_q} provides a closed form solution to the minimax program \eqref{eq:omni-twoplayer-minimax} for multiple quantile levels. Finally, Section \ref{subsec:omni_multi_q_online} puts the results together and provides a sample efficient algorithm for omniprediction of multiple quantile level forecasts.

\cite{fissler2016multiq} proved that a consistent (proper) loss for multiple quantile levels can be written as a weighted sum of consistent (proper) loss for each quantile levels, under mild regularity conditions.


\subsection{Decomposition of consistent scoring rules for multiple quantile levels}\label{subsec:decomp_multi_q}
Note: \cite{osband1985} considers $F \in \cf$ to be a non-negative measures on a finite domain. \cite{fissler2016multiq} extends this to a broader class of distribution functions on $\R^d$.

\begin{theorem}[Theorem 3.2 in \cite{fissler2016multiq}, Extension of Theorem 2.1 in \cite{osband1985}]
Let $\cf$ be a convex class of distribution functions on $\mathsf{O} \subseteq \R^d$. Let $T: \cf \to \mathsf{A} \subseteq \R^k$ be a surjective, elicitable and identifiable functional with a strict $\cf$-identification function $V: \mathsf{A} \times \mathsf{O} \to \R^k$ and a strictly $\cf$-consistent scoring function $S: \mathsf{A} \times \mathsf{O} \to \R$. If the assumptions (V1) and (S1) hold, then there exists a matrix-valued function $h: \mathrm{int}(\mathsf{A}) \to \R^{k \times k}$ such that for $l \in \{1, \ldots, k\}$
\begin{align}
\partial_l \bar{S}(x, F) = \sum_{m=1}^{k} h_{lm}(x) \bar{V}_m(x, F)
\end{align}
for all $x \in \mathrm{int}(\mathsf{A})$ and $F \in \cf$. If in addition, assumption (V2) holds, then $h$ is continuous. Under the additional assumptions (V3) and (S2), the function $h$ is locally Lipschitz continuous.
\end{theorem}

Theorem above establish necessary condition on the level of expected score $\bar{S}(x,F)$. If the class $\cf$ is rich enough (F1) and the scoring and identification function are smooth enough (VS1), we have the following necessary condition for $S$ which holds pointwise.

\begin{prop}[Proposition 3.5 in \cite{fissler2016multiq}]
Let $\cf$ be convex. Assume that $\mathrm{int}(\mathsf{A}) \subseteq \R^k$ is a star domain and let $T: \cf \to \mathsf{A}$ be a surjective, elicitable and identifiable functional with a strict $\cf$-identification function $V: \mathsf{A} \times \mathsf{O} \to \R^k$ and a strictly $\cf$-consistent scoring function $S: \mathsf{A} \times \mathsf{O} \to \R$. Suppose that assumptions (V1), (V2), (S1), (F1) and (VS1) hold. Let $h$ be the matrix valued function appearing at (3.2). Then, the scoring function $S$ is necessarily of the form
\begin{align}
S(x, y) = \sum_{r=1}^{k} \sum_{m=1}^{k} \int_{z_r}^{x_r} h_{rm}(x_1, \ldots, x_{r-1}, v, z_{r+1}, \ldots, z_k) \times V_m(x_1, \ldots, x_{r-1}, v, z_{r+1}, \ldots, z_k, y) \, dv + a(y)
\end{align}
for almost all $(x, y) \in \mathsf{A} \times \mathsf{O}$ for some star point $z = (z_1, \ldots, z_k) \in \mathrm{int}(\mathsf{A})$ and some $\cf$-integrable function $a: \mathsf{O} \to \R$. On the level of the expected score $\bar{S}(x, F)$, the equation holds for all $x \in \mathrm{int}(A)$, $F \in \hat{\cf}$.
\end{prop}

\paragraph{Assumption (V4).} Let assumption (V3) hold. For all $r \in \{1, \ldots, k\}$ and for all $t \in \mathrm{int}(\mathsf{A}) \cap T(\cf)$ there are $F_1, F_2 \in T^{-1}(\{t\})$ such that
\[
\partial_l \bar{V}_l(t, F_1) = \partial_l \bar{V}_l(t, F_2) \quad \forall l \in \{1, \ldots, k\} \setminus \{r\}, \qquad \partial_r \bar{V}_r(t, F_1) \neq \partial_r \bar{V}_r(t, F_2).
\]

Then, Proposition 4.1 and Corollary 4.2 in \cite{fissler2016multiq} shows that with additional assumption (V4) above, $h$ is necessarily diagonal.
\begin{theorem}[Corollary 4.2 in \cite{fissler2016multiq}]
Let $\cf$ be convex. Suppose that $T = (T_1, \ldots, T_k): \cf \to \mathsf{A}$ is a functional with 1-identifiable components having oriented strict $\cf$-identification functions $V_m: \mathsf{A_m} \times \mathsf{O} \to \R$. Assume the interior of $\mathsf{A}:=T(\cf) \subseteq \mathsf{A}_1 \times \cdots \times \mathsf{A}_k$ is a star domain and that assumptions (V1), (V3), (V4), (S2), (F1) and (VS1) hold. Then, a scoring function $S: \mathsf{A} \times \mathsf{O} \to \R$ is strictly $\cf$-consistent for $T$ if and only if it is of the form
\begin{align}
    S(x_1, \ldots, x_k, y) = \sum_{m=1}^{k} S_m(x_m, y),
\end{align}
for almost all $(x,y) \in \mathsf{A} \times \mathsf{O}$, where $S_m: \mathsf{A}_m \times \mathsf{O} \to \R$, $m \in \{1, \ldots, k\}$, are strictly $\cf$-consistent scoring functions for $T_m$.
\end{theorem}



\subsection{Separate omniprediction for each quantile level}\label{subsec:separate_multi_q}
\cite{fakoor2023flexible} showed that post-sorting and isotonic projection decrease the loss for \textbf{unweighted} weighted sums of pinball losses at different quantile levels. Unfortunately, post-sorting does not achieve the same for \textbf{weighted} sums of pinball losses.

Define the pinball loss at quantile level $\tau$ as $\rho_\tau(x) := \tau x\indi{x \geq 0} +(1-\tau)|x|\indi{x < 0} = (\tau - \indi{x < 0})x$. Then define the loss function 
\[
\ell(x_1, x_2) := \E_Y [w_\alpha \rho_\alpha (y-x_1) + w_\beta \rho_\beta (y-x_2)].
\] 
Consider the case $\alpha < \beta$. We would like $\ell(x_1, x_2) - \ell(x_2, x_1) \geq 0$ for $x_1 > x_2$. 
\paragraph{Counterexample} Let $Y \sim \text{Ber}(1/2)$ and $0 < x_2 < x_1 < 1$. Then, 
\begin{align*}
\ell(x_1, x_2) - \ell(x_2, x_1) 
& = w_\alpha \E_Y \left[(\alpha - \indi{y < x_1})(y-x_1) - (\alpha - \indi{y < x_2})(y-x_2)\right] + \\ 
& \qquad w_\beta \E_Y \left[(\beta - \indi{y < x_2})(y-x_2) - (\beta - \indi{y < x_1})(y-x_1) \right] \\
& = w_\alpha (\alpha - 1/2)(x_2 - x_1) + w_\beta (\beta - 1/2)(x_1 - x_2) \\
& = (x_1 - x_2)(w_\beta (\beta - 1/2) - w_\alpha (\alpha - 1/2))
\end{align*}
Note that the second equality uses the fact that $\indi{y < x_1} = \indi{y < x_2}$. When $\alpha$ and $\beta$ lie on the same side of $1/2$, there exist $(w_\alpha, w_\beta)$ for which the improvement in loss becomes negative.
Conversely, if $(w_\alpha, w_\beta)$ does not satisfy any of the above conditions, then there exists $(Y, x_1, x_2)$ such that post-sorting increases the loss.

\smallskip
If we solve the minimax program \textbf{separately for each quantile level}, quantile crossing may occur (or maybe NOT due to the structure of $f(X)$ that it is a valid probability forecast and thus no quantile crossing occurs). Unfortuately, the following proposition shows that post-sorting does not always reduce loss for \textbf{unequally} weighted sums of pinball losses.

\subsubsection{Characterizaion of weighted quantile loss that post-sorting does decrease the loss}
\begin{prop}
As above, define a weighted quantile loss as
\[
\ell(x_1, x_2) := \E_Y [w_\alpha \rho_\alpha (y-x_1) + w_\beta \rho_\beta (y-x_2)].
\]
If $(w_\alpha, w_\beta)$ satisfies one of the following conditions, then post-sorting does not increase the loss:
\begin{enumerate}
  \item $w_\alpha = w_\beta$
  \item $w_\alpha < w_\beta$ and $(1-\alpha)w_\alpha \geq (1-\beta)w_\beta$
  \item $w_\alpha > w_\beta$ and $\beta w_\beta \geq \alpha w_\alpha$.
\end{enumerate}
Conversely, if $(w_\alpha, w_\beta)$ does not satisfy any of the above conditions, then there exists $(Y, x_1, x_2)$ such that post-sorting increases the loss.
\end{prop}

\begin{proof}
\begin{align*}
\ell(x_1, x_2) - \ell(x_2, x_1) 
& = w_\alpha \E_Y \left[(\alpha - \indi{y < x_1})(y-x_1) - (\alpha - \indi{y < x_2})(y-x_2) \right] + \\ 
& \qquad w_\beta \E_Y \left[(\beta - \indi{y < x_2})(y-x_2) - (\beta - \indi{y < x_1})(y-x_1) \right] \\
& = w_\alpha E_Y \left[\left\{-\alpha(x_1 - x_2) + \indi{y < x_1}x_1 - \indi{y < x_2}x_2 - \indi{x_2 \leq y < x_1}y \right\}\right] + \\
& \qquad w_\beta E_Y \left[ \left\{\beta(x_1 - x_2) + \indi{y < x_2}x_2 - \indi(y < x_1)x_1 + \indi{x_2 \leq y < x_1}y \right\} \right] \\
& = \E_Y \left[\left\{-\alpha(x_1 - x_2) + \indi{x_2 \leq y < x_1}(x_1 - y) + \indi{y < x_2}(x_1 - x_2)\right\} \right] w_\alpha + \\
& \qquad \E_Y \left[\left\{\beta(x_1 - x_2) - \indi{x_1 \leq y < x_2}(x_1 - y) - \indi{y < x_2}(x_1 - x_2)\right\} \right] w_\beta 
\end{align*}
Denote the coefficient of $w_\alpha, w_\beta$ as $c_\alpha, c_\beta$ respectively. Notice that $c_\alpha + c_\beta = (\beta-\alpha)(x_1 - x_2) > 0$. Therefore $\ell(x_1, x_2) - \ell(x_2, x_1) > 0$ if $w_\alpha = w_\beta$ (Condition I).
Denote $A = \P(y < x_2)$, $B = \P(x_2 \geq y < x_1)$ and observe that $\E_Y \indi{x_2 \geq y < x_1}(x_1 - y) \in [0, B(x_1 - x_2)]$.
We now consider Condition II: $w_\alpha < w_\beta$ and $(1-\alpha)w_\alpha \geq (1-\beta)w_\beta$. 
\begin{align*}
\ell(x_1, x_2) - \ell(x_2, x_1) 
& = \left(w_\alpha(A-\alpha) + w_\beta(\beta-A)\right)(x_1 - x_2) - (w_\beta - w_\alpha)\E_Y \indi{x_2 \leq y < x_1}(x_1 - y) \\
& \geq -(w_\beta - w_\alpha)A + \beta w_\beta - \alpha w_\alpha - (w_\beta - w_\alpha)B(x_1 - x_2) \\
& \geq -(w_\beta - w_\alpha)A + (w_\beta - w_\alpha) - (w_\beta - w_\alpha)B(x_1 - x_2) \\
& \geq (w_\beta - w_\alpha)(1-A-B)(x_1 - x_2) \geq 0.
\end{align*}
Note that $\beta w_\beta - \alpha w_\alpha \geq w_\beta - w_\alpha$ follows from the condition and $A+B = \P(Y < x_1) \leq 1$.
Condition III is similar.
{\color{red} If we put this propoisition in the paper, add constructing counterexample for $(w_\alpha, w_\beta)$ that does not satisfy any of the above conditions.}
\end{proof}

Alternatively, we prove another class of loss functions where post-sorting does not increase the loss. Due to \cite{fissler2016multiq}, a loss function that is consistent for multiple quantile levels can be written as a weighted sum of consistent (proper) loss for each quantile levels, under mild regularity conditions:
\begin{align} \label{eq:multi_q_consistent_loss}
\ell(\{x_i\}_{i=1}^N, y) = \E_Y \sum_{i=1}^{N} w^i (\indi{y < x_i} - \tau_i)(g_i(x_i) - g_i(y)),  
\end{align}
where $g_i$ is a non-decreasing function.
\begin{prop}
If a loss function $\ell$ defined as \eqref{eq:multi_q_consistent_loss} satisfies $w_i = w$ and $g_i(x) = g(x)$ for all $i \in [N]$, then post-sorting does not increase the loss.
\end{prop}
\begin{proof}
Due to additivity of the loss function, it suffices to show $\ell(x_1, x_2, y) - \ell(x_2, x_1, y) \geq 0$ for $x_1 > x_2$ where $x_i$ corresponds to the $\tau_i$-level quantile estimate. Without loss of generality, assume $w=1$.
\begin{align*}
\ell(x_1, x_2, y) & - \ell(x_2, x_1, y) 
= \E_Y [ (\indi{y < x_1} - \tau_1)(g_1(x_1) - g_1(y)) - (\indi{y < x_2} - \tau_1)(g_1(x_2) - g_1(y)) + \\
& \qquad (\indi{y < x_2} - \tau_2)(g_2(x_2) - g_2(y)) - (\indi{y < x_1} - \tau_2)(g_2(x_1) - g_2(y))] \\
& = \E_Y [\tau_1(g_1(x_2)-g_1(x_1)) + \indi{y < x_1}g_1(x_1) - \indi{y < x_2}g_1(x_2) - \indi{x_2 \leq y < x_1}g_1(y) + \\
& \qquad \tau_2(g_2(x_1)-g_2(x_2)) + \indi{y < x_2}g_2(x_2) - \indi{y < x_1}g_2(x_1) + \indi{x_2 \leq y < x_1}g_2(y)]
\end{align*}
Now using the fact that $g_1 \equiv g_2 \equiv g$, most of the terms cancel out and we have 
\begin{align*}
\ell(x_1, x_2, y) - \ell(x_2, x_1, y) = (\tau_2 - \tau_1)(g(x_1) - g(x_2)) \geq 0.
\end{align*}
{\color{blue} Just to add, in general case with $w_i=w$ but $g_i$ can be different, the difference of loss is as following:
\begin{align*}
\ell(x_1, x_2, y) - \ell(x_2, x_1, y) 
& = \tau_2(g_2(x_1)-g_2(x_2)) - \tau_1(g_1(x_1)-g_1(x_2)) - \int_{x_2}^{x_1} (\P(Y < x))(g_2'(x) - g_1'(x)) dx \\
& = (\tau_2 - \tau_1)(g_1(x_1) - g_1(x_2)) - \int_{x_2}^{x_1} (\P(Y < x) - \beta)(g_2'(x) - g_1'(x)) dx  
\end{align*}
Note that $g_i(x_1) - g_i(x_2) \geq 0$ since $g_i$ is non-decreasing.
}
\end{proof}








\subsection{Solution for joint minimax program} \label{subsec:omni_multi_q}
Simlarly to Section \ref{subsec:omni_single_q}, this subsection provides a closed form solution to the minimax program \eqref{eq:omni-twoplayer-minimax}. 
Due to Corollary 4.2 in \cite{fissler2016multiq}, a loss function that is consistent for multiple quantile levels can be written as a weighted sum of consistent (proper) loss for each quantile levels, under mild regularity conditions. For a set of quantile levels $\tau_1 < \tau_2 < ... < \tau_N$ and positive measures $\{H_{\tau_n}\}_{n=1}^N$, any scoring function that is consistent for the multiple quantile levels can be written as
\begin{align}\label{eq:multi_q_consistent_score}
  S(x,y) = \sum_{n=1}^N \int_{-\infty}^{\infty} S_i^n(x,y) dH_{\tau_n}(\theta),
\end{align}
where $S_i^n(x,y) = (\one(y<x)-\tau_n)(\one(\theta_i<x)-\one(\theta_i<y))$ for $n \in [N]$ and $i \in \{0, \ldots, m-1\}$.


% Similarly to previous section, we define forecasts $\{\hat{f}_{\theta_i}^\tau\}_{i=0}^{m-1}$ that empirically minimized the losses $\{S_{\tau, \theta_i}\}_{i=0}^{m-1}$ for $\tau=\alpha, \beta$. For given $P \in \Delta_m$, denote the $\tau$-level quantile of $P$ as $P_\tau$. Then, consider $\cd(\Delta_m)$, the set of distributions over forecast $P \in \Delta_m$. The joint minimax program we want to solve is
% \[
% \min_{\tilde{P} \in \cd(\Delta_m)} \max_{P_y \in \Delta_m} \sum_{\tau \in \{\alpha, \beta\}}\sum_{i=0}^{m-1} w_i^\tau \E_{P\sim \tilde{P}, Y \sim P_y}[S_{\tau,\theta_i}(q_\tau(P),Y) - S_{\tau,\theta_i}(\hat{f}_{\theta_i}^\tau,Y)].
% \]

% Similarly to Lemma \ref{lem:minimax_single_q_neg}, we have the following lemma:
% \begin{lemma}
% \[
% \min_{P \in \Delta_m} \max_{P_y \in \Delta_m} \sum_{\tau \in \{\alpha, \beta\}}\sum_{i=0}^{m-1} w_i^\tau \E_{p\sim P, Y \sim P_y}[S_{\tau,\theta_i}(q_\tau(p),Y) - S_{\tau,\theta_i}(\hat{f}_{\theta_i},Y)] 
% \leq 0
% \]
% \end{lemma}
% \begin{proof}
% Similar to the proof of Lemma \ref{lem:minimax_single_q_neg}.
% \end{proof}

% Notice that the expection only depends on $\tilde{P}$ through $q_\alpha(P)$ and $q_\beta(P)$. Therefore, with abbreviating $\hat{f}_{\theta_i}^\tau,Y$ as $\hat{f}_i^\tau$, we can rewrite the program as
% \begin{align}\label{eq:multi_minimax_program}
% \min_{P_\alpha, P_\beta \in \Delta_m} \max_{P_y \in \Delta_m} \sum_{\tau \in \{\alpha, \beta\}}\sum_{i=0}^{m-1} w_i^\tau \E_{p_\tau \sim P_\tau, Y \sim P_y}[S_{\tau,\theta_i}(p_\tau,Y) - S_{\tau,\theta_i}(\hat{f}_i^\tau,Y)],
% \end{align}
% subject to the constraint $p_\alpha \leq p_\beta$. To provide a roadmap: to satisfy this constraint, we first solve the minimax program for $P_\alpha$ and $P_\beta$, where it can be proved that the resulting solutions satisfy the condition that $P_\alpha$ is stochastically smaller than $P_\beta$. Finally, we couple $P_\alpha$ and $P_\beta$ in increasing order to form a joint distribution that maintains the condition $p_\alpha \leq p_\beta$.

% Now, we solve the joint minimax program.
% \begin{lemma}\label{lem:minimax_sol_two_q}
% Given $\hat{f}_i^\tau$ for $i =0,...,m\!-\!1$ and $\tau = \alpha, \beta$, define the quantity $V$ as
% \begin{align} \label{eq:V_def}
% V = \min_{j \in [m]} \left( \sum_{i=j}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} + \sum_{i=0}^{j-1} w_i^\beta (1 - \indi{\theta_i < \hat{f}_i^\beta})\right) \geq 0
% \end{align}
% and let $j^*$ be \textbf{any} index that minimizes the quantity.

% Then, the value of the minimax program is $-(\beta-\alpha)V \leq 0$ and the solution is given by 
% \begin{align*}
%   P_y^* &= \alpha\delta_0 + \beta\delta_1 + (\beta-\alpha)\delta_{j^*/m} \\
%   P^*_\tau &= C_\tau \delta_{k_\tau^*/m} + (1-C_\tau) \delta_{(k_\tau^*+1)/m}, \quad \tau = \alpha, \beta,
% \end{align*}
% where
% \begin{align*}
%   k_\alpha^* &= \min\left\{k \mid \sum_{i=0}^k w_i^\alpha \geq \sum_{i=0}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - V \right\} \\
%   k_\beta^* &= \min\left\{k \mid \sum_{i=0}^k w_i^\beta > \sum_{i=0}^{m-1} w_i^\beta \indi{\theta_i < \hat{f}_i^\beta} + V \right\} \\
%   C_\alpha & = \frac{1}{w_{k_\alpha^*}^\alpha} \left( \sum_{i=0}^{k_\alpha^*} w_i^\alpha - \left(\sum_{i=0}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - V\right)\right)\\
%   C_\beta & = \frac{1}{w_{k_\beta^*}^\beta} \left( \sum_{i=0}^{k_\beta^*} w_i^\beta - \left(\sum_{i=0}^{m-1} w_i^\beta \indi{\theta_i < \hat{f}_i^\beta} + V\right)\right),
% \end{align*}
% Moreover, for any $j^*$ that achieves the minimum in \eqref{eq:V_def}, it holds that $k_\alpha^* < j^* \leq k_\beta^*$, which implies that $P_\alpha$ is stochastically smaller than $P_\beta$.
% \end{lemma}

% % PROOF START
% \begin{proof}
% We first prove that $k_\alpha^* < j^* \leq k_\beta^*$. Plugging in  
% \[
% V = \sum_{i=j}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} + \sum_{i=0}^{j-1} w_i^\beta (1 - \indi{\theta_i < \hat{f}_i^\beta}),
% \] 
% into the definition of $k_\alpha^*$, we observe that $j^*-1$ satisfies the inequality and thus $k_\alpha^* \leq j^*-1$.
% \begin{align*}
% \sum_{i=0}^{j^*-1} w_i^\alpha
% & \geq \sum_{i=0}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - V \\ 
% & = \sum_{i=0}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - \sum_{i=j}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - \sum_{i=0}^{j-1} w_i^\beta (1 - \indi{\theta_i < \hat{f}_i^\beta}, 
% \end{align*}
% which is equivalent to 
% \begin{align*}
% \sum_{i=0}^{j^*-1} w_i^\alpha (1-\indi{\theta_i < \hat{f}_i^\alpha}) + w_i^\beta (1-\indi{\theta_i < \hat{f}_i^\beta}) \geq 0.
% \end{align*}
% This inequality holds since indicators are always smaller than or equal to $1$.

% Similarly, we can show that $j^*-1$ does not satisfy the inequality inside the definition of $k_\beta^*$, which implies that $k_\beta^* > j^*-1$ and thus $k_\beta^* \geq j^*$.
% \smallskip

% Now, we prove that $O(P_\alpha^*, P_\beta^*, P_y^*)$ is the minimax solution. Denote the objective function by 
% \[O(P_\alpha, P_\beta, P_y) = \sum_{\tau \in \{\alpha, \beta\}}\sum_{i=0}^{m-1} w_i^\tau \E_{p_\tau \sim P_\tau, Y \sim P_y}[S_{\tau,\theta_i}(p_\tau,Y) - S_{\tau,\theta_i}(\hat{f}_i^\tau,Y)].
% \]
% In a similar vein to the proof of Lemma \ref{lem:minimax_sol_single_q}, we show $O(P_\alpha^*, P_\beta^*, P_y^*) = \max_{P_y} O(P_\alpha^*, P_\beta^*, P_y)$ then show $O(P_\alpha^*, P_\beta^*, P_y^*) = \min_{P_\alpha, P_\beta \in \Delta_m} O(P_\alpha, P_\beta, P_y^*)$.

% Following the decomposition \eqref{eq:oppy_q}, $O(P_\alpha, P_\beta, P_y)$ can be written as
% \[
% O(P_\alpha, P_\beta, P_y) = \sum_{\tau \in \{\alpha, \beta\}}\sum_{i=0}^{m-1} w_i^\tau \E_{p_\tau \sim P_\tau, Y \sim P_y}[\one(Y \leq \theta_i < p_\tau) - \tau\one(\theta_i<p_\tau) - \one(Y \leq \theta_i < \hat{f}_i^\tau)] + C_\tau,
% \]
% where $C_\tau =\tau \sum_{i=0}^{m-1} q_i^\tau \indi{\theta_i < \hat{f}_i^\tau}$ which does not depend on $P_\tau$ or $P_y$.

% Using this decomposition, we prove $O(P_\alpha^*, P_\beta^*, P_y^*) = \max_{P_y} O(P_\alpha^*, P_\beta^*, P_y)$. Let $P_y(\frac{j}{m})=p_{yj}$ for $j=0,...,m$. Then, $O(P_\alpha^*, P_\beta^*, P_y)$ is rephrased as the following:
% \begin{align*}
% O(P_\alpha^*, P_\beta^*, P_y) 
% & = \sum_{\tau \in \{\alpha, \beta\}}\E_{P_\tau^*} \left[\sum_j p_{yj} \sum_{i=j}^{m-1} w_i^\tau \left( \indi{\theta_i < p_\tau} - \indi{\theta_i < \hat{f}_i^\tau}\right)\right] + C(P_\tau^*),
% \end{align*}
% where $C(P_\tau^*)$ only depends on $P_\tau^*$ and does not depend on $P_y$.

% Plugging in $P_\tau^*$, the summand can be expressed as 
% \begin{align*}
% A_j := \E_{P_\tau^*} & \left[\sum_{i=j}^{m-1} w_i^\tau \left( \indi{\theta_i < p_\tau} - \indi{\theta_i < \hat{f}_i^\tau}\right)\right] \\
% & = 
% \begin{cases}
% -\sum_{i=0}^{j-1} w_i^\tau (1-\indi{\theta_i < \hat{f}_i^\tau}) + V \indi{\tau=\alpha} - V\indi{\tau=\beta} & \quad j \leq k_\tau^* \\
% - \sum_{i=j}^{m-1} w_i^\tau \indi{\theta_i < \hat{f}_i^\tau} & \quad j > k_\tau^* \\
% \end{cases} 
% \end{align*}

% This leads to 
% \begin{align*}
% A_j = 
% \begin{cases}
% - \sum_{i=0}^{j-1} w_i^\alpha (1-\indi{\theta_i < \hat{f}_i^\alpha}) - \sum_{i=0}^{j-1} w_i^\beta (1-\indi{\theta_i < \hat{f}_i^\beta}) & \quad j \leq k_\alpha^* \\
% - \sum_{i=j}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - \sum_{i=j}^{m-1} w_i^\beta \indi{\theta_i < \hat{f}_i^\beta} & \quad j > k_\beta^* \\
% - \sum_{i=j}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - \sum_{i=0}^{j-1} w_i^\beta (1-\indi{\theta_i < \hat{f}_i^\beta}) + V & \quad k_\alpha^* < j \leq k_\beta^*
% \end{cases}
% \end{align*}
% Notice that $A_j$ is non-increasing on $j \leq k_\alpha^*$ and non-decreasing on $j > k_\beta^*$. $A_0 = 0$ and $A_m = 0$ is the maximum value of $A_j$ in these ranges, respectively. Also note that $A_j \leq 0$ for $k_\alpha^* < j \leq k_\beta^*$ due to the definition of $V$ and $A_{j^*} = 0$ since $k_\alpha^* < j^* \leq k_\beta^*$.

% To sum up, $P_y^*$ achieves the maximum value of $O(P_\alpha^*, P_\beta^*, P_y)$ since it puts mass only on $j=0, j^*, m$, which are the points that maximize $A_j$.

% Lastly, we show that $O(P_\alpha^*, P_\beta^*, P_y^*) = \min_{P_\alpha, P_\beta} O(P_\alpha, P_\beta, P_y^*)$. This follows directly from the consistency of $S_{\tau,\theta_i}$ losses, since $k_\alpha^* / m$ and $(k_\alpha^*+1) / m$ are both $\alpha$-level quantile of $P_y^*$ and $k_\beta^* / m$ and $(k_\beta^*+1) / m$ are both $\beta$-level quantile of $P_y^*$.
% \end{proof}
% % PROOF END

% \paragraph{Minor details}
% In definition of $k_\alpha^*$ and $k_\beta^*$, we use $\geq$ and $>$, respectively. If $k_\alpha^*$ is also defined using $>$, the difference occurs when there exists $j$ that satisfies $\sum_{i=0}^{j-1} w_i^\alpha = \sum_{i=0}^{m-1} w_i^\alpha \indi{\theta_i < \hat{f}_i^\alpha} - V$. 
% \begin{enumerate}
%   \item $\forall i \in [m], w_i^\alpha > 0$. In this case, $k_\alpha^*$ differs by 1, but $P_\alpha^* = \delta_{j/m}$ remains the same.
%   \item $\exists i \in [m], w_i^\alpha = 0$. In this case, $P_\alpha^*$ is also different. For example, let $w_0^\alpha = \alpha$, $w_1^\alpha = 0$, $w_2^\alpha > 0$, then definition using $\geq$ gives $P_\alpha^* = \delta_{1/m}$ (smallest possible $\alpha$-level quantile) while definition using $>$ gives $P_\alpha^* = \delta_{2/m}$ (largest possible $\alpha$-level quantile).
% \end{enumerate}


% \subsection{Solving joint minimax program for arbitrary number of quantile levels}
% Now we extend the result to the case of arbitrary number of quantile levels. We denote $N$ as the number of quantile levels and $\tau_1 < \tau_2 < ... < \tau_N$ as the quantile levels. 

In a similar vein to the notation in Section \ref{subsec:omni_single_q}, let $\hat{f}_i^n$ be the best forecast in $\cf$ that minimizes the losses $\{S_i^n\}$ for $i =0,...,m\!-\!1$ and $n \in [N]$. {\color{blue} Omitted details of discretization etc. that is straightforward extension from single quantile level case} Then, the minimax program for multiple quantile level omniprediction is given by

\[
\min_{\tilde{P} \in \cd(\Delta_m)} \max_{P_y \in \Delta_m} \sum_{n=1}^N \sum_{i=0}^{m-1} w_i^n \E_{P\sim \tilde{P}, Y \sim P_y}[S_i^n(q_{\tau_n}(P),Y) - S_i^n(\hat{f}_i^n(t),Y)],
\]
where $q_{\tau_n}(P)$ is the $\tau_n$-level quantile of $P$ and $S_i^n(x, Y) = (\one(Y < x)-\tau_n)(\one(\theta_i<x)-\one(\theta_i<Y))$ as defined previously. We can rewrite the program as follows:
\[
\min_{P_1, P_2, ..., P_N \in \Delta_m} \max_{P_y \in \Delta_m} \sum_{n=1}^N \sum_{i=0}^{m-1} w_i^n \E_{p_n \sim P_n
, Y \sim P_y}[S_i^n(p_n,Y) - S_i^n(\hat{f}_i^n,Y)],
\]
with the constraint that the joint distribution ($P_1, P_2, ..., P_N$) always satisfies the ordering of the samples $p_1 \leq p_2 \leq ... \leq p_N$.

Before getting into the minimax solution, we first prove the following lemmas.

\begin{lemma}\label{lem:jn_sort}
Define the quantity $V_n$ for $n \in [N-1]$ as
\begin{align} \label{eq:Vn_def}
V_n := \min_{j \in [m]} \left( \sum_{i=j}^{m-1} \sum_{s=1}^{n} w_i^s \indi{\theta_i < \hat{f}_i^s} + \sum_{i=0}^{j-1} \sum_{s=n+1}^{N}  w_i^s (1 - \indi{\theta_i < \hat{f}_i^s})\right) \geq 0
\end{align}
and $V_0 = V_N := 0$.
Let $J_n^*$ be the set of indices $j \in [m]$ that minimizes the $V_n$. 
\smallskip \\
Then, there exists a sorted sequence $0=j_0^* \leq j_1^* \leq ... \leq j_{N-1}^* \leq j_N^* = m$ such that $j_n^* \in J_n^*$ for $n \in [N-1]$.
\end{lemma}

\begin{proof}
Suppose there exists a pair of indices $n, n+1$ such that $j_n^* > j_{n+1}^*$. Using the definition of $V_n$, we have 
\begin{align*}
j_n^* &= \argmin_{j \in [m]} \left( \sum_{i=j}^{m-1} \sum_{s=1}^{n} w_i^s \indi{\theta_i < \hat{f}_i^s} + \sum_{i=0}^{j-1} \sum_{s=n+2}^{N}  w_i^s (1 - \indi{\theta_i < \hat{f}_i^s}) + \sum_{i=0}^{j-1} w_i^{n+1} (1 - \indi{\theta_i < \hat{f}_i^{n+1}})\right) \\
j_{n+1}^* &= \argmin_{j \in [m]} \left( \sum_{i=j}^{m-1} \sum_{s=1}^{n+1} w_i^s \indi{\theta_i < \hat{f}_i^s} + \sum_{i=0}^{j-1} \sum_{s=n+2}^{N}  w_i^s (1 - \indi{\theta_i < \hat{f}_i^s}) + \sum_{i=j}^{m-1} w_i^{n+1}\indi{\theta_i < \hat{f}_i^{n+1}}\right).
\end{align*}
Two expressions share the first two terms and differ in the last term. We abbreviate these terms as following:
\begin{align*}
C_j & := \sum_{i=j}^{m-1} \sum_{s=1}^{n} w_i^s \indi{\theta_i < \hat{f}_i^s} + \sum_{i=0}^{j-1} \sum_{s=n+2}^{N}  w_i^s (1 - \indi{\theta_i < \hat{f}_i^s}) \\
D_j & := \sum_{i=0}^{j-1} w_i^{n+1} (1 - \indi{\theta_i < \hat{f}_i^{n+1}}) \\
E_j & := \sum_{i=j}^{m-1} w_i^{n+1}\indi{\theta_i < \hat{f}_i^{n+1}}.
\end{align*}
Note that $D_j$ is non-decreasing in $j$ and $E_j$ is non-increasing in $j$.
Since $j_n^*$ and $j_{n+1}^*$ are the indices that minimize the $V_n$ and $V_{n+1}$, respectively, we have $C_{j_n^*} + D_{j_n^*} \leq C_{j_{n+1}^*} + D_{j_{n+1}^*}$ and $C_{j_n^*} + E_{j_n^*} \geq C_{j_{n+1}^*} + E_{j_{n+1}^*}$. This implies that 
\[
E_{j_{n+1}^*} - E_{j_n^*} \leq C_{j_n^*} - C_{j_{n+1}^*} \leq D_{j_{n+1}^*} - D_{j_n^*}.
\]
Because of the monotonicity of $D_j$ and $E_j$ and the assumption that $j_n^* > j_{n+1}^*$, the leftmost term should be non-negative and the rightmost term should be non-positive. Therefore, we obtain 
\[
C_{j_n^*} - C_{j_{n+1}^*} = D_{j_n^*} - D_{j_{n+1}^*} = E_{j_n^*} - E_{j_{n+1}^*} = 0 \quad \Rightarrow j_{n+1}^* \in J_n^*, \,\, j_n^* \in J_{n+1}^*.
\]
By choosing $j_{n+1}^*$ as a minimizer of $V_n$ and $j_n^*$ as a minimizer of $V_{n+1}$, we resolve the unsorted pair of indices. Repeating this process yields a sorted sequence $0=j_0^* \leq j_1^* \leq ... \leq j_{N-1}^* \leq j_N^* = m$ and this proves the existence of sorted sequence.
\\
Due to its existence, we can simply obtain a sorted sequence by choosing $j_n^* = \min J_n^*$ for all $n \in [N]$.
\end{proof}

\begin{lemma} \label{lem:Pn_def}
Given a sorted sequence $0=j_0^* \leq j_1^* \leq ... \leq j_{N-1}^* \leq j_N^* = m$, there exists a distribution $P_n^*$ for $n \in [N]$ of the form
\begin{align}\label{eq:Pn_def}
P_n^* = (1-C_n)\delta_{k_n / m} + C_n\delta_{(k_n+1)/m},
\end{align}
such that 
\begin{enumerate}
  \item $j_{n-1}^* \leq k_n$
  \item $k_n < j_n^*$ if $j_{n-1}^* \neq j_n^*$ and $k_n = j_n^*$ with $C_n=0$ if $j_{n-1}^* = j_n^*$.
  \item The support of $P_n^*$ is contained in $[j_{n-1}^*/m, j_n^*/m]$.
  \item $\E_{p_n \sim P_n^*} \left[ \sum_{i=0}^{m-1} w_i^n \left( \indi{\theta_i < p_n} - \indi{\theta_i < \hat{f}_i^n} \right) \right] = V_{n-1}-V_n$.
\end{enumerate}
\end{lemma}
\begin{proof}
In this proof, we abbreviate $\indi{\theta_i < \hat{f}_i^n}$ by $\one_i^n$ for $i \in [m]$ and $n \in [N]$.
Abbreviate the expression inside the definition of $V_n$ as follows:
\begin{align}\label{eq:Vn_j_def}
V_n(j) = \sum_{i=j}^{m-1} \sum_{s=1}^{n} w_i^s \one_i^n + \sum_{i=0}^{j-1} \sum_{s=n+1}^{N}  w_i^s (1 - \one_i^n)  \quad \forall j \in [m], n \in [N].
\end{align}
Note that $V_n = V_n(j_n^*)$ for all $n \in [N-1]$ and that $V_n(j) \geq V_n(j_n^*)$ for all $j \in [m]$.
\\
With the fact that $\indi{\theta_i < k/n} = \indi{i < k}$, the last condition in the lemma statement is equivalent to 
\begin{align} 
\sum_{i=0}^{k_n-1} w_i^n + C_n w_{k_n^*}^n = \sum_{i=0}^{m-1} w_i^n \one_i^n - V_n + V_{n-1} = \sum_{i=0}^{j_{n-1}^*-1} w_i^n + V_n(j_{n-1}^*) - V_n(j_n^*), \label{eq:Pn_eq}
\end{align}
where the last equality used the fact that $\sum_{i=0}^{m-1} w_i^n \one_i^n + V_{n-1}(j) = \sum_{i=0}^{j-1} w_i^n + V_n(j)$ with $j=j_{n-1}^*$.
\smallskip \\
Now we divide the cases into three cases. 
First, consider the case where $j_{n-1}^* = j_n^*$. In this case, simply $k_n = j_{n-1}^*$ with $C_n=0$ satisfies the equation \eqref{eq:Pn_eq}. Therefore, $P_n^* = \delta_{j_{n-1}^*/m}$ satisfies the conditions.
Second, consider the case where $j_{n-1}^* < j_n^*$ but $V_n(j_{n-1}^*) = V_n(j_n^*)$. $k_n = j_{n-1}^*$ with $C_n=0$ again satisfies the equation \eqref{eq:Pn_eq} and $k_n = j_{n-1}^* < j_n^*$ in this case.
Lastly, consider the case where $V_n(j_{n-1}^*) > V_n(j_n^*)$. We have 
\begin{align*}
  \sum_{i=0}^{j_{n-1}^*-1} w_i^n 
  & < \sum_{i=0}^{j_{n-1}^*-1} w_i^n + V_n(j_{n-1}^*) - V_n(j_n^*) \\
  & = \sum_{i=0}^{m-1} w_i^n \one_i^n - V_n + V_{n-1} \\
  & = \sum_{i=0}^{j_{n}^*-1} w_i^n + V_{n-1}(j_{n-1}^*) - V_{n-1}(j_n^*) 
  \leq \sum_{i=0}^{j_{n}^*-1} w_i^n,
\end{align*}

where two equalities used the fact that $\sum_{i=0}^{m-1} w_i^n \one_i^n + V_{n-1}(j) = \sum_{i=0}^{j-1} w_i^n + V_n(j)$ with $j=j_n^*$ on the second term of the equation \eqref{eq:Pn_eq}.
This implies that there exists a $j_{n-1}^* \leq k_n < j_n^*$ such that 
\begin{align*}
  \sum_{i=0}^{k_n} w_i^n \geq \sum_{i=0}^{m-1} w_i^n \one_i^n - V_n + V_{n-1} \quad \text{and} \quad \sum_{i=0}^{k_n-1} w_i^n < \sum_{i=0}^{m-1} w_i^n \one_i^n - V_n + V_{n-1}.
\end{align*}
With such $k_n$, we define $P_n^*$ with $C_n = \frac{1}{w_{k_n}^n} \left( \sum_{i=0}^{m-1} w_i^n \one_i^n - V_n + V_{n-1} - \sum_{i=0}^{k_n-1} w_i^n \right)$ and this satisfies the conditions since $k_n+1 \leq j_n^*$.
\end{proof}





Now we provide the solution to the minimax program \eqref{eq:omni-twoplayer-minimax}.
\begin{theorem}\label{thm:minimax_negative_multi_q}
Given quantile levels $\tau_1 < \tau_2 < ... < \tau_N$, quantile forecasts $\hat{f}_i^n$ for $i =0,...,m\!-\!1$ and $n \in [N]$, define $V_n$ $n \in [N-1]$ as in equations \eqref{eq:Vn_def}, with $V_0 = V_N := 0$. Let $\{j_n^*\}_{n=1}^{N-1}$ be a sorted sequence of indices that minimizes the $V_n$ for $n \in [N-1]$ with $j_0^* = 0$ and $j_N^* = m$ where the existence of the sequence is guaranteed by Lemma \ref{lem:jn_sort}. 
\smallskip \\
Then, $P_n^*$ for $n \in [N]$ given by \eqref{eq:Pn_def} with 
\[
P_y^* = \tau_1 \delta_0 + (1-\tau_N)\delta_1 + \sum_{n=1}^{N-1}(\tau_{n+1}-\tau_n)\delta_{j_t^*/m}
\]
solves the minimax program \eqref{eq:omni-twoplayer-minimax} and the value of the minimax program is 
\[
-\sum_{n=1}^{N-1}(\tau_{n+1}-\tau_n)V_n \leq 0.
\]

% Then, the value of the minimax program is $-\sum_{t=1}^{N-1}(\tau_{t+1}-\tau_t)V_t \leq 0$ and the solution is given by 
% \begin{align*}
%   P_y^* &= \tau_1 \delta_0 + (1-\tau_N)\delta_1 + \sum_{t=1}^{N-1}(\tau_{t+1}-\tau_t)\delta_{j_t^*/m} \\
%   P_t^* &= C_t \delta_{\underline{k_t^*}/m} + (1-C_t) \delta_{(\underline{k_t^*}+1)/m}, \quad t \in [N],
% \end{align*}
% where
% \begin{align*}
%   \underline{k_t^*} &= \min\left\{k \mid \sum_{i=0}^k w_i^t \geq \sum_{i=0}^{m-1} w_i^t \indi{\theta_i < \hat{f}_i^t} - V_t + V_{t-1} \right\} \\
%   \overline{k_t^*} &= \min\left\{k \mid \sum_{i=0}^k w_i^t > \sum_{i=0}^{m-1} w_i^t \indi{\theta_i < \hat{f}_i^t} - V_t + V_{t-1} \right\} \\
%   C_t & = \frac{1}{w_{\underline{k_t^*}}^t} \left( \sum_{i=0}^{\underline{k_t^*}} w_i^t - \left(\sum_{i=0}^{m-1} w_i^t \indi{\theta_i < \hat{f}_i^t} - V_t + V_{t-1}\right)\right),
% \end{align*}
% for $t \in [N]$ with $V_0 = V_N := 0$.

% Moreover, for any $j_t^*$ that achieves the minimum in \eqref{eq:Vt_def}, it holds that $\underline{k_t^*} < j_t^* \leq \overline{k_{t+1}^*}$, \sout{which implies that $P_t^*$ is stochastically smaller than $P_{t+1}^*$}. {\color{red} I'm confident that $\underline{k_t^*} \leq \underline{k_{t+1}^*}$ also holds, so that $\underline{k_t^*}$ doesn't have crossing issue.}
\end{theorem}
\begin{proof}
Denote the minimax objective function by 
\[O(\{P_n\}_{n=1}^N, P_y) = \sum_{n=1}^N \sum_{i=0}^{m-1} w_i^n \E_{p_n \sim P_n, Y \sim P_y}[S_{\tau_n,\theta_i}(p_n,Y) - S_{\tau_n,\theta_i}(\hat{f}_i^n,Y)].
\]
In a similar vein to the proof of Lemma \ref{lem:minimax_sol_single_q}, we show $O(\{P_n^*\}_{n=1}^N, P_y^*) = \max_{P_y} O(\{P_n^*\}_{n=1}^N, P_y)$ then show $O(\{P_n^*\}_{n=1}^N, P_y^*) = \min_{P_n \in \Delta_m, n\in[N]} O(\{P_n\}_{n=1}^N, P_y^*)$.

Following the decomposition \eqref{eq:oppy_q}, $O(\{P_n\}_{n=1}^N, P_y)$ can be written as
\[
O(\{P_n\}_{n=1}^N, P_y) = \sum_{n=1}^N \sum_{i=0}^{m-1} w_i^n \E_{p_n \sim P_n, Y \sim P_y}[\one(Y \leq \theta_i < p_n) - \tau_n \one(\theta_i<p_n) - \one(Y \leq \theta_i < \hat{f}_i^n)] + C_n,
\]
where $C_n =\tau_n \sum_{i=0}^{m-1} w_i^n \indi{\theta_i < \hat{f}_i^n}$ which does not depend on $P_n$ or $P_y$.

Using this decomposition, we prove $O(\{P_n^*\}_{n=1}^N, P_y^*) = \max_{P_y} O(\{P_n^*\}_{n=1}^N, P_y)$. Let $P_y(\frac{j}{m})=p_{yj}$ for $j=0,...,m$. Then, $O(\{P_n^*\}_{n=1}^N, P_y)$ is rephrased as the following:
\begin{align}\label{eq:O_Pstar_Py_decomp}
O(\{P_n^*\}_{n=1}^N, P_y) 
& = \sum_{n=1}^N \E_{p_n \sim P_n^*} \left[\sum_j p_{yj} \sum_{i=j}^{m-1} w_i^n \left( \indi{\theta_i < p_n} - \indi{\theta_i < \hat{f}_i^n}\right)\right] + C(P_n^*),
\end{align}
where $C(P_n^*) = - \tau_n \E_{p_n \sim P_n^*} \sum_{i=0}^{m-1} w_i^n (\indi{\theta_i < p_n} - \indi{\theta_i < \hat{f}_i^n})$ only depends on $P_n^*$ and does not depend on $P_y$.

Plugging in $P_n^*$ and abbreviating $\indi{\theta_i < \hat{f}_i^n}$ with $\one_i^n$, the summand can be expressed as 
\begin{align*}
A_j^n := \E_{P_n^*} & \left[\sum_{i=j}^{m-1} w_i^n \left( \indi{\theta_i < p_n} - \one_i^n\right)\right] \\
& = 
\begin{cases}
-\sum_{i=0}^{j-1} w_i^n (1-\one_i^n) - V_n + V_{n-1} & \quad j \leq k_n^* \\
- \sum_{i=j}^{m-1} w_i^n \one_i^n & \quad j > k_n^* \\
\end{cases} 
\end{align*}

This leads to 
\begin{align*}
A_j := \sum_{n=1}^N A_j^n = 
\begin{cases}
-\sum_{n=1}^N \sum_{i=0}^{j-1} w_i^n(1-\one_i^n) + V_0 & \quad j \leq k_1 \\
-\sum_{n=1}^\nu \sum_{i=j}^{m-1} w_i^n \one_i^n - \sum_{n=\nu+1}^{N} \sum_{i=0}^{j-1} w_i^n (1-\one_i^n) + V_\nu & \quad k_\nu < j \leq k_{\nu+1}, \,\, \nu \in [N-1] \\
-\sum_{n=1}^N \sum_{i=j}^{m-1} w_i^n \one_i^n + V_N & \quad j > k_N
\end{cases}
\end{align*}
Notice that $A_j$ is non-increasing on $j \leq k_1$ and non-decreasing on $j > k_N$. $A_0 = 0$ and $A_m = 0$ is the maximum value of $A_j$ in these ranges, respectively. Next, observe that $A_j \leq 0$ for all $j=0,1,...,m$ since $V_n$ is the minimum value that $\sum_{\nu=1}^n \sum_{i=j}^{m-1} w_i^n \one_i^\nu + \sum_{\nu=n+1}^{N} \sum_{i=0}^{j-1} w_i^{\nu} (1-\one_i^{\nu})$ can achieve by its definition. It suffices to show that $A_{j_n^*} = 0$ for $n \in [N-1]$ since $P_y^*$ only puts mass on these points. Note that $A_{j_0} = A_0 = 0$ and $A_{j_N} = A_m = 0$.

From the first and second condition in the statement of Lemma \ref{lem:Pn_def}, we have $k_\nu < j_\nu^* \leq k_{\nu+1}$ if $j_{\nu-1}^* \neq j_\nu^*$ and $j_{\nu-1}^* = j_\nu^*= k_\nu$ if $j_{\nu-1}^* = j_\nu^*$, for $\nu \in [N-1]$. In the former case, we obtain $A_{j_\nu^*} = 0$ from $k_\nu < j \leq k_{\nu+1}$ case in the definition of $A_j$ above. In the latter case, $j_\nu^* = k_\nu$ does not fall into the range $(k_\nu, k_{\nu+1}]$. Still, from $k_{\nu-1} < j \leq k_{\nu}$ case ($j \leq k_1$ case if $\nu=1$) in the definition of $A_j$ , we have
\begin{align*}
A_{j_n^*} 
& = -\sum_{n=1}^{\nu-1} \sum_{i=j}^{m-1} w_i^n \one_i^n - \sum_{n=\nu}^{N} \sum_{i=0}^{j-1} w_i^n (1-\one_i^n) + V_{\nu-1} \\
& =  - V_{\nu-1}(j_n^*) + V_{\nu-1} = -V_{\nu-1}(j_{n-1}^*) + V_{\nu-1} = 0,
\end{align*}
where $V_n(j)$ is defined as equation \eqref{eq:Vn_j_def}. Therefore, $A_{j_n^*} = 0$ for all $n \in [N-1]$ and $O(\{P_n^*\}_{n=1}^N, P_y^*) = \max_{P_y} O(\{P_n^*\}_{n=1}^N, P_y)$.

Next, we show that $O(\{P_n^*\}_{n=1}^N, P_y^*) = \min_{P_n \in \Delta_m, n\in[N]} O(\{P_n\}_{n=1}^N, P_y^*)$. This follows directly from the consistency of $S_{\tau,\theta_i}$ losses and the third condition in Lemma \ref{lem:Pn_def}. Any point in the support of $P_n^*$ is $\tau_n$-level quantile of $P_y^*$ since $P_y(Y \leq j_{n-1}^*/m) = \tau_n$ and $P_y(Y \geq j_n^*/m) = \tau_n$.

Lastly, we compute the value of the minimax program. Decomposition \eqref{eq:O_Pstar_Py_decomp} can be rewritten as 
\[
O(\{P_n^*\}_{n=1}^N, P_y) = \sum_{j} p_{yj} A_j + \sum_{n=1}^N C(P_n^*).
\]
Since $P_Y^*$ only puts mass on points $j/m$ such that $A_j = 0$, plugging in $P_y^*$ into the equation above yields
\begin{align*}
O(\{P_n^*\}_{n=1}^N, P_y^*) 
&= \sum_{n=1}^N C(P_n^*) = -\sum_{n=1}^N \tau_n \E_{p_n \sim P_n^*} \sum_{i=0}^{m-1} w_i^n (\indi{\theta_i < p_n} - \one_i^n) \\
&  = -\sum_{n=1}^N \tau_n (V_{n-1} - V_n) = -\sum_{n=1}^{N-1}(\tau_{n+1}-\tau_n)V_n \leq 0,
\end{align*}
where the second from the last equality used the fourth condition in Lemma \ref{lem:Pn_def}.
\end{proof}


\subsection{Sample efficient algorithm for omniprediction of multiple quantile level forecasts}\label{subsec:omni_multi_q_online}

\begin{algorithm}
  \caption{Two-player game based multiple quantile level online omniprediction} \label{alg:omni-twoplayer_online_multi_q}
  \begin{algorithmic}[1]
  \State \textbf{Data:} Data stream $\{Y_t\}_{t=1}^T$, quantile levels $\tau_1 < \tau_2 < ... < \tau_N$, hyperparameters $m, F \in \mathbb{N}$, $\eta_w, \eta_f > 0$, base forecaster predictions $\hat{f}_j^n(t)$: $\tau_n$-level quantile estimate of $f_j$ for $j \in [F]$ and $n \in [N]$;
  \State For $t=1$,$w_i^n(t) = \frac{1}{mN}$, $\hat{f}_i^n(t) = f_1^n(t)$, for all $i \in \{0, \ldots, m-1\}$ and $n \in [N]$;
  \State $v_{i,j}^n(1) = \frac{1}{F}$, for all $i \in \{0, \ldots, m-1\}$ and $j \in \{1, \ldots, F\}$ and $n \in [N]$;
  \For{$t = 1, \ldots, n$}
    \State \textbf{1) Make prediction at time $t$}:
      \State Define $V_0 = V_N = 0$, $j_0^* = 0$, $j_N^* = m$;
      \State Define $\one_i^s(t) = \indi{\theta_i < \hat{f}_i^s(t)}$ for $i \in \{0, \ldots, m-1\}$ and $s \in [N]$.
      \For{$n=1, \ldots, N-1$}
      \State Compute $V_n(j)$ for $j \in [m]$:
        \(
        V_n(j) = \sum_{i=j}^{m-1} \sum_{s=1}^{n} w_i^s \one_i^s(t) + \sum_{i=0}^{j-1} \sum_{s=n+1}^{N}  w_i^s (1 - \one_i^s(t))
        \)
      \State Compute $V_n$ and $j_n^*$:
        \begin{align*}
          V_n = \min_{j \in [m]} V_n(j), \qquad
          j_n^* = \min\left\{j_{n-1}^* \leq j \leq m \mid V_n(j) = V_n \right\}
        \end{align*}
      \EndFor \vspace{-0.2cm}\\
      \For{$n=1, \ldots, N$}
        \If{$V_n(j_{n-1}^*) = V_n(j_n^*)$}
          \State $\hat{P}_t^n = \delta_{j_{n-1}^*/m}$;
        \Else
          \State Define $B_k := \sum_{i=0}^{k-1} w_i^n(t) - \sum_{i=0}^{m-1}w_i^n(t) \one_i^n(t)$
          \State Find $j_{n-1}^* \leq k_n < j_n^*$ s.t. $B_{k_n} < V_{n-1} - V_n \leq B_{k_n+1}$ (Existence proved in Lemma \ref{lem:Pn_def})
          \State $\hat{P}_t^n = (1-C_n)\delta_{k_n/m} + C_n\delta_{((k_n+1)/m)}$, where $C_n = \left( V_{n-1} - V_n - B_{k_n} \right) / w_{k_n}^n$
        \EndIf
      \EndFor
      \State \textbf{Output} $\hat{P}_t = \{\hat{P}_t^n\}_{n=1}^N$;  \vspace{-0.1cm}\\
      \State \textbf{2) Update the weights for each $S_{i}^n = (\one(y<x)-\tau_n)(\one(\theta_i<x)-\one(\theta_i<y))$}:
          \State $w_i^n(t+1) = \frac{w_i^n(t) \exp\bigl(\eta \big(\mathbb{E}_{p \sim \hat{P}_t^n}[S_i^n(p, Y_t)] 
          - S_i^n(\hat{f}_i^n(t), Y_t)\big)\bigr)}{\sum_{i=0}^{m-1} \sum_{n=1}^N w_i^n(t) \exp\bigl(\eta \big(\mathbb{E}_{p \sim \hat{P}_t^n}[S_i^n(p, Y_t)] - S_i^n(\hat{f}_i^n(t), Y_t)\big)\bigr)}, \forall n \in [N], i \in \{0, \ldots, m-1\};$ \vspace{-0.1cm}\\
      \State \textbf{3) Update the best competitor function for each $S_{i}^n$}:
      \State $v_{i,j}^n(t+1) = \frac{v_{i,j}^n(t) \exp\bigl(-\eta_f S_i^n(\hat{f}_j^n(t), Y_t)\bigr)}{\sum_{j=1}^F v_{i,j}^n(t) \exp\bigl(-\eta_f S_i^n(\hat{f}_j^n(t), Y_t)\bigr)}, \quad \forall j \in [F], n \in [N], i \in \{0, \ldots, m-1\};$
      \For{$n = 1, \ldots, N$}
        \For{$i = 0, \ldots, m-1$}
          \State Sample $j_i^n(t+1) \in [F] \sim v_{i,\cdot}^n(t+1)$ and update $\hat{f}_i^n(t+1) = f_{j_i^n(t+1)}^n(t+1)$;
        \EndFor
      \EndFor
  \EndFor
  \end{algorithmic}
  \end{algorithm}
  


\begin{theorem}
  \label{thm:omni-twoplayer_online_multi_q}
  For a set of quantile levels $\tau_1 < \tau_2 < ... < \tau_N$, let $\cs$ denote the class of scoring functions with representation \eqref{eq:multi_q_consistent_loss} with positive measures $\{H_{\tau_n}\}_{n=1}^N$ such that $H_{\tau_n}(\R) \leq 1, \forall n \in [N]$ (the set of \textit{all} scoring functions that are consistent for the multiple quantile levels under mild regularity conditions). Consider a class of competitors $\cf$ where each forecaster $f \in \cf$ provides $\{\tau_n\}_{n=1}^N$-level quantile forecasts $\{f^n(t)\}_{n=1}^N$. With the target values $Y_t$, forecaster predictions $f^n(t)$ for $t \in [T], n \in [N], f \in \cf$ each taking values in a discretized grid of size $m$, and the learning rate $\eta_w = O(\sqrt{\frac{\log (mN)}{T}})$ and $\eta_f = O(\sqrt{\frac{\log |\cf|}{T}})$, the output $\hat{P}_t = \{\hat{P}_t^n\}_{n=1}^N$ from Algorithm \ref{alg:omni-twoplayer_online_multi_q} achieves the following omniprediction error:
  \begin{align*}
  \sup_{S \in \cs,\, f \in \cf} \frac{1}{T} \sum_{n=1}^N \sum_{t=1}^T \E_{p \sim \hat{P}_t^n} [S(p, Y_t)] - \E[S(f^n(t), Y_t)]
  \leq O\left(\sqrt{\frac{\log mN|\cf|}{T}}\right)
  \end{align*}
\end{theorem}

\begin{proof}
  Straightforward extension of Theorem \ref{thm:omni-twoplayer_online_q}, using theorem \ref{thm:minimax_negative_multi_q}.
\end{proof}